---
title       : MPG Model Selector
subtitle    : Coursera Developing Data Product Project
author      : Yang Yaw Chang
job         : MOOC Student
framework   : io2012 #***{io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js #***{highlight.js, prettify, highlight}
hitheme     : tomorrow     # 
widgets     : []         # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## MPG Model Selector

This is a peer assessment project for Developing Data Product course by Coursera. Following are to be delivered in this assignment:
- A shiny application hosted in Shiny server:
[Shiny App](https://y2charlie.shinyapps.io/DevelopingDataProductShiny/)
- A 5 pages Slidify presentation hosted in Rpub.
- Git repository containing the source file:
        - here

--- .class #id 

## The Shiny Application

This application aims to demonstrate the basic implemetation of Shiny application.The application is hosted at

The application  offers the following:
- Allow user to choose from 1 of 3 regressor combinations available.
- Update Adjusted Rsquare, model coefficient and residual plot based on the chosen regressor combination.

--- .class #id 

## The Data and Modelling technique

mtcars data is used in assignment. Linear regression technique is used for comparison of model fitness against different combination of regressors.

```{r, echo=TRUE}
head(mtcars)
```

--- .class #id 

## The Input and Output

3 regressor combinations are made available as radio button option. Following is the sample output
```{r, echo=FALSE}
model <- lm(mpg ~ cyl + hp + wt + am, data=mtcars);
summary(model)$coef
summary(model)$adj.r.squared
par(mfrow = c(2, 2)) 
plot(model)
```






